\hypertarget{interface_voxel_busters_1_1_runtime_serialization_1_1_i_runtime_serializable_activator}{}\section{I\+Runtime\+Serializable\+Activator}
\label{interface_voxel_busters_1_1_runtime_serialization_1_1_i_runtime_serializable_activator}\index{I\+Runtime\+Serializable\+Activator@{I\+Runtime\+Serializable\+Activator}}


Implement this interface to control instance creation of serialized type. Static method with signature\+: object Create\+Instance (\hyperlink{class_voxel_busters_1_1_runtime_serialization_1_1_runtime_serialization_info}{Runtime\+Serialization\+Info} \+\_\+info) is invoked when creating serialized object instance. \hyperlink{class_voxel_busters_1_1_runtime_serialization_1_1_runtime_serialization_info}{Runtime\+Serialization\+Info} contains all the initializer values that were formerly serialized. So get all the initializer values from \hyperlink{class_voxel_busters_1_1_runtime_serialization_1_1_runtime_serialization_info}{Runtime\+Serialization\+Info} and create object instance.  




\subsection{Detailed Description}
Implement this interface to control instance creation of serialized type. Static method with signature\+: object Create\+Instance (\hyperlink{class_voxel_busters_1_1_runtime_serialization_1_1_runtime_serialization_info}{Runtime\+Serialization\+Info} \+\_\+info) is invoked when creating serialized object instance. \hyperlink{class_voxel_busters_1_1_runtime_serialization_1_1_runtime_serialization_info}{Runtime\+Serialization\+Info} contains all the initializer values that were formerly serialized. So get all the initializer values from \hyperlink{class_voxel_busters_1_1_runtime_serialization_1_1_runtime_serialization_info}{Runtime\+Serialization\+Info} and create object instance. 

